Proposed Solution

### 2017-04-18 OOPSLA17/secs/intro.tex
autocommit

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply our learning process to learn an abundant set of rules 
specifying various properties that hold on the given training set. 
The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.

The rules, in general, 
specify which properties keywords in configuration files need to satisfy.
\ruzica{examples of properties}

@@

Our learning algorithm surmounts both of these shortcomings present in 
existing tools.  \app implements a learning
algorithm inspired by {\em association rule
learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration files~\cite{configdataset}. Those are real-world reported misconfigurations. 
A file in the training set might contain several different errors and these errors only appear 
in a small percentage of files. 
We first translate those file into an intermediary typed language. 
With with every type, we associate a set of very general interfaces. 
The user does not need to provide them - they are internally associated with the types. 
The learner then instantiates those interfaces with the keywords appearing in 
the training set. However, since files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are correct enough,
\app employs a graph analysis to refine the set learned rules.
\app analyzes the rule graph to rank the importance and relevance of the learned rules.

We have implemented a tool, \app, and evaluated it on almost 1000 real-
world configuration files from Github.
We demonstrate that we are able to detect known errors, based on 
StackOverflow posts, in this data set.
Furthermore, we find compelling evidence that out optimizations are 
effective, for example using probabilistic types \ruzica{this is the first time you mention them, so i don't know what is that}

removes 1023 false 
positives errors reports to reduce the total error reports to 324.
The rule graph analysis drastically improves the ranking of importance of 
the error reports, which allows users to more quickly correct the most 
critical misconfigurations.
Additionally, \app scales linearly, whereas 
a previous tool~\cite{santolucitoCAV} showed exponential slow downs on 
the same benchmark set.

>>>>

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply our learning process to learn an abundant set of rules 
specifying various properties that hold on the given training set. 
The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
The rules, in general, specify which properties such as, one kewyord must appear before another, or the value of one keyword should always be greater than another.

@@

Our learning algorithm surmounts both of these shortcomings present in 
existing tools.  \app implements a learning
algorithm inspired by {\em association rule
learning}~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
A file in the training set might contain several different errors, but errors only appear 
in a small percentage of files. 
We first translate those file into an intermediary typed language.
\app then learns rules based on the inferred types of the keywords from the training set.
However, since the files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are correct enough,
\app employs a graph analysis to refine the set learned rules.
\app analyzes the rule graph to rank the importance and relevance of the learned rules.

We have implemented a tool, \app, and evaluated it on almost 1000 real-
world configuration files from Github.
We demonstrate that we are able to detect known errors, based on 
StackOverflow posts, in this data set.
Furthermore, we find compelling evidence that out optimizations are 
effective
For example, we introduce a probabilistic type inference system that removes 1023 false 
positives errors reports to reduce the total error reports to 324.
The rule graph analysis drastically improves the ranking of importance of 
the error reports, which allows users to more quickly correct the most 
critical misconfigurations.
Additionally, \app scales linearly, whereas 
a previous tool~\cite{santolucitoCAV} showed exponential slow downs on 
the same benchmark set.
